%---------------------------------------------------------------------
%
%                      resumen.tex
%
%---------------------------------------------------------------------
%
% Contiene el capítulo del resumen.
%
% Se crea como un capítulo sin numeración.
%
%---------------------------------------------------------------------

\chapter{Abstract}
\cabeceraEspecial{Resumen}

Electronic systems nano scale components are susceptible to high energy particles collisions. This energy particles could interfere in those   electronic devices processes and therefore modifying its internal data. This includes all microprocessors used in devices for general or specific purposes.

In some application areas those particles are found in greater amount, and greater energy, therefore  the probability of a fault produced by a collision will increase and the system operation will become unpredictable.

This project deals to implement a Central Processor Unit capable of properly working even when it is suffering from these interferences. The project has been addressed in three tasks:

\begin{enumerate}
  \item Firstly, the Control Processor Unit will be implemented. Implementation is based on the DLX architecture studied in the Computers Architecture courses and adapting the chosen instruction set.
  \item Secondly, Fault Tolerance techniques will be applied on the CPU.
  \item Finally the design will be tested, checking that fault tolerance has been successfully implemented, applied to the CPU and has increased the reliability of the system.
\end{enumerate}

\endinput




